Report on Late Winter2013 Production: Image Differencing\vspace{-2ex}

### 2013-04-01 W13report.tex
QUick addendum on per-sensor configs vs. shallow slope in fp heat map

We note that the config at the minimum MSE value is
not always the same config that yields the lowest numbers of false detections.  
Table \ref{tab-bestconfig_MSE} lists the configs
at the minimum of the MSE for the control sample (compare to Table~\ref{tab-bestconfig10}).
%
We have also 
looked at per--sensor MSE values and per--sensor false positive rates.  In both cases, 
the config that produces the minimum number of false positives is variable
from sensor to sensor.  It is worth investigating how much the false positive rate
per chip goes down if per sensor optimal configs are used instead of per visit optimal
configs.
%
When we look at the MSE per chip and compare with the minimum false positive config we 
find good agreement, in general.  The findings are summarized in Table \ref{tab-MSE_persensor}.  Because
the MSE is sensitive to over fitting, we observe that it tends to lower complexity configs
even if the false positive rate is slightly higher.  We will continue to investigate this metric
in Summer 2013.

@@

{XXX: Figure 4 : we should note that flat is good as we are less
  sensitive to getting the tuning perfect\\

>>>>

We note that the config at the minimum MSE value is
not always the same config that yields the lowest numbers of false detections.  
Table \ref{tab-bestconfig_MSE} lists the configs
at the minimum of the MSE for the control sample (compare to Table~\ref{tab-bestconfig10}).
%
We have also 
looked at per--sensor MSE values and per--sensor false positive rates.  In both cases, 
the config that produces the minimum number of false positives is variable
from sensor to sensor.  It is worth investigating how much the false positive rate
goes down if per--sensor optimal configs are used instead of per--visit optimal
configs.  On the other hand, because the false positive rate is relatively flat beyond a critical 
configuration (Figure~\ref{fp_heatmap}), we are not strongly sensitive to getting the per--sensor
tunings perfect.
%
When we look at the MSE per chip and compare with the minimum false positive config we 
find good agreement, in general.  The findings are summarized in Table \ref{tab-MSE_persensor}.  Because
the MSE is sensitive to over fitting, we observe that it tends to lower complexity configs
even if the false positive rate is slightly higher.  We will continue to investigate this metric
in Summer 2013.

@@
